\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{titlesec, xcolor, enumitem}
\usepackage{hyperref}

% Define section formatting
\titleformat{\section}{\large\bfseries\color{black}}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\LARGE \textbf{CURRICULUM VITAE}} \\[0.5cm]
    \textbf{Priscilla Acquah, B.Sc.} \\
    Obuasi-West, Obuasi Municipal, Ashanti Region, Ghana \\
    A0-015-4467 \\
    \texttt{+233546015674 | acquahpee19@gmail.com} 
\end{center}

\section*{PERSONAL PROFILE}
I am a highly motivated, professional, and industrious individual committed to utilizing my skills to help a team achieve its goals. I believe in hard work, teamwork, and dedication. I am keen on continuous learning and improvement by taking advice from others.

\section*{SKILLS}
\begin{itemize}
    \item Microsoft Office Suite: Proficient in Word, Excel, and PowerPoint.
    \item GIS Tools: Experienced in ArcMap and QGIS.
    \item CAD Software: Competent in AutoCAD.
\end{itemize}

\section*{WORK EXPERIENCE}
\textbf{Graceland Surveys} \hfill October 2024 – Present \\
\textit{Survey Department}
\begin{itemize}
    \item Setting out land boundaries.
    \item Preparing land documents.
    \item Georeferencing land boundaries.
\end{itemize}

\textbf{National Service} \hfill October 2023 – November 2023 \\
\textit{Secretary at the Assistant Headmaster (Academic)’s Office}

\section*{INSTRUMENT PROFICIENCY}
\begin{itemize}
    \item Using GNSS receivers for data collection, staking out, and traversing.
    \item Using Total Station for data collection, staking out, and traversing.
    \item Using Dumpy level for levelling.
\end{itemize}

\section*{EDUCATION}
\textbf{University of Mines and Technology (UMaT), Tarkwa} \\
B.Sc. in Geomatic Engineering \hfill January 2021 – September 2024 \\

\textbf{Serwa Nyarko Girls Senior High School, Dichemso-Kumasi} \\
WAEC Certificate in Science \hfill October 2016 – June 2019 \\

\textbf{Rams Junior High School, Abompe-Obuasi} \\
BECE \hfill October 2013 – June 2016

\section*{REFERENCES}
\textbf{Assoc. Prof. Cynthia Borkai Boye} \\
Lecturer, Geomatic Engineering Department \\
University of Mines and Technology, Post Office Box 237, Tarkwa, Ghana \\
\texttt{cboye@umat.edu.gh} \\
 Tel: +233 244444179 \\[0.2cm]
 
 \noindent\textbf{Sharrif Yakubu Mambo} \\ 
Assistant Headmaster (Academic) \\
Obuasi Senior High Technical School, Post Office Box 237, Obuasi, Ghana \\
Tel: +233 244959500

\end{document}
