\documentclass[a4paper,12pt]{letter}
\usepackage[left=1in, right=1in, top=0.2in, bottom=1in]{geometry}
\usepackage{graphicx}

\signature{\\ Desmond Kangah}
\address{1443 Brightside Dr, Campus Crossing \\ desmondkangah98@gmail.com \\ +1 2254336635}

\begin{document}

\begin{letter}{Geospatial Intelligence and National Security Technologies, \\ Washington, DC}

\opening{Dear Hiring Manager,}

I am excited to apply for the \textbf{Geospatial Intelligence Intern} position at \textbf{Geospatial Intelligence and National Security Technologies}. With a strong background in geospatial engineering, remote sensing, and AI-driven geospatial analysis, I am eager to contribute my expertise to your team. My experience in GIS, machine learning, and spatial software development aligns well with your organization's mission of leveraging geospatial intelligence for national security.

Currently pursuing my \textbf{MSc in Civil Engineering (Geodesy and Geomatics)} at Louisiana State University, I have been actively engaged in cutting-edge research on InSAR data processing for land subsidence monitoring. As a \textbf{Teaching and Research Assistant}, I have developed GIS-based applications for urban planning and contributed to AI-driven land use classification projects. My hands-on experience with satellite imagery, drone surveys, and spatial analysis tools such as Google Earth Engine, QGIS, and ArcGIS equips me with the technical proficiency needed for this internship.

Beyond my technical skills, I have held leadership roles, including serving as \textbf{Vice President of the Tertiary Student Association of Ahanta}, where I organized workshops and seminars on geospatial technologies. Additionally, my experience as a \textbf{Chief Surveyor at MAC Partners} and my work with the \textbf{Ghana Highway Authority} have strengthened my ability to manage and analyze large-scale geospatial data for critical decision-making.

I am eager to apply my skills and passion for geospatial intelligence to support your organization's objectives. I welcome the opportunity to further discuss how my experience can contribute to your team. Thank you for your time and consideration. I look forward to your response.

%\closing{Sincerely,}
Sincerely, \\
Desmond Kangah.
\end{letter}

\end{document}
